### 2014-11-10 CVPR/Source/occlusion.tex
Started related works section

In this section, we introduce our representation of 3D traffic participants and our modeling of object-object occlusion relationships.

@@

\paragraph{Image formation}
Given the above occupancy representation of the scene, a point on an object is observed in the camera when precisely two conditions are satisfied. First, the backprojected ray from the observed image pixel is transmitted through free space until it reaches the object. Second, the ray encounters an opaque enough object surface and is reflected. More formally, the probability of observation of a point $\bx_j$ on object $O_i$ is given by
\begin{align}
  P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}
\end{align}
The reflection term ensures the presence of an object to constitute the observation, while the transmission probability allows us to model occlusions.

@@

\paragraph{Transmission probability}
A model for transmission of light through a material of thickness $\alpha$, density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
\begin{align}
I(x) = I_0 e^{-\beta\rho\alpha}.
\end{align}
%
In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function $\occftot = \sum_i \occf$. Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$. Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
%
\begin{align}
  \!\!\!\! P_{\textit{transmission}}(\lambda + d\lambda) = P_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
\end{align}
%
For an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
\begin{align}
P^j_{\textit{transmission}}(\lambda) = \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda},
\label{eq:ptrans-integral}
\vspace{\eqs}
\end{align}
where $\displaystyle\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to $\lambda$.\footnote{A product integral is a simple integral in log domain: 
\vspace{-0.2cm}
\begin{equation}
\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
\end{equation}
}

@@

>>>>

In this section, we introduce our representation of 3D traffic participants and our modeling of object-object occlusion relationships. We refer the reader to Figure [[FIGURE]] for an illustration of the proposed concepts.

@@

\paragraph{Image formation}
Given the above occupancy representation of the scene, a point on an object is observed in the camera when precisely two conditions are satisfied. First, the backprojected ray from the observed image pixel is transmitted through free space until it reaches the object. Second, the ray encounters an opaque enough object surface and is reflected. More formally, the probability of observation of a point $\bx_j$ on object $O_i$ is given by
\begin{align}
P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}.
\label{eq:imgform}
\end{align}
The reflection probability ensures the presence of an object to constitute the observation, while the transmission probability allows us to model occlusions. The forms of these two functions are described next.

@@

\paragraph{Transmission probability}
A model for transmission of light through a material of thickness $\alpha$, density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
\begin{align}
I(x) = I_0 e^{-\beta\rho\alpha}.
\end{align}
%
In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function $\occftot = \sum_i \occf$. Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$. Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
%
\begin{align}
  \!\!\!\! P_{\textit{transmission}}(\lambda + d\lambda) = P_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
\end{align}
%
For an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
\begin{align}
P^j_{\textit{transmission}}(\lambda) = \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda},
\label{eq:ptrans-integral}
\end{align}
where $\displaystyle\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to $\lambda$.\footnote{A product integral is a simple integral in log domain: 
\vspace{-0.2cm}
\begin{equation}
\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
\end{equation}
}

@@

%\paragraph{Probabilistic occlusion levels}
%With the above modeling and using \eqref{eq:imgform},

### 2014-11-10 CVPR/Source/related.tex
Started related works section

>>>>

\paragraph{Occlusion handling}
Several works in object detection consider occlusion by training a detector on visible parts of the object \cite{Gao_etal_2011,Wu_Nevatia_2007}. In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}. By necessity, such frameworks are often a discrete representation of occlusion behavior, for example, in the form of a collection of occlusion masks derived from object configurations discretized over viewpoint. In constrast to these works, our occlusion modeling is also fully 3D, but allows for a continuous representation. Further, to derive 3D information, we do not use CAD models, rather we derive a probabilistic formulation based on physical insights.

Occlusion handling in tracking \cite{Wu_Nevatia_2007,Milan_etal_2014}.

\paragraph{3D localization and scene understanding}
Occlusion handling in scene understanding \cite{Zia_etal_2013,Zia_etal_2014}.

\paragraph{Multibody SFM}

\paragraph{Motion segmentation}
